\texttt{davos}: The Python package smuggler

### 2022-04-05 paper/main.tex
rework intro for clarity

% --------------------------------------------- MOTIVATION & SIGNIFICANCE ----------------------------------------------
\section{Motivation and significance}
Modern open science practices encourage sharing code and data to enable others to explore, reproduce, learn from, and build upon existing work. Scientists, researchers, and educators produce many different forms of research-related code (e.g., experiments, data analyses, tutorials, demos) that they may seek to share with a wide range of audiences, including collaborators, students, the broader scientific community, and the general public. Python has become one of the most widely used and fastest-growing scientific programming languages by offering both powerful research functionality and high-level accessibility \cite{MullEtal15}. In addition to the language’s intuitive, readable grammar and large standard library, the Python ecosystem provides an extensive data science toolkit designed to facilitate rapid development and collaboration, including platforms for interactive programming (e.g., Project Jupyter, \cite{KluyEtal16}; Google Colaboratory), community-maintained libraries for data manipulation (e.g., \texttt{NumPy} \cite{HarrEtal20}, \texttt{SciPy} \cite{VirtEtal20}, \texttt{Pandas} \cite{McKi10}) and visualization (e.g., \texttt{Matplotlib} \cite{Hunt07}, \texttt{seaborn} \cite{Wask21}), and myriad other tools.

However, this also presents a challenge to sharing reproducible scientific Python code: different versions of a given package or library can behave differently, use different syntax, add or drop support for specific functions or other libraries, address (or introduce) bugs, and so on. While these issues are present to some extent in any language or ecosystem, they have a particular impact on the Python community due to its unusually rapid growth relative to other languages. Ensuring stable and reproducible results over time and across users therefore typically requires ensuring that shared code is always run with a specific set of versions for each package used.

>>>>

% --------------------------------------------- MOTIVATION & SIGNIFICANCE ----------------------------------------------
\section{Motivation and significance}
Modern scientific research often involves writing code for a variety of purposes throughout the research process, from designing experiments, to analyzing and visualizing data, to presenting findings via tutorials or public demos. One requirement common to nearly all research-related code it that its behavior and/or outputs must remain consistent and predictable every time it is run, both over time and across users. For example, this stability can be critical to ensuring that data are collected under constant conditions (e.g., across recordings, trials, or subjects) and that statistical analyses yield accurate, consistent results. Additionally, modern open science practices encourage sharing code and data publicly to enable others to explore, reproduce, learn from, and build upon existing work. Scientists, researchers, and educators may seek to share research-related code with a wide range of audiences including collaborators, students, the broader scientific community, and the general public.

Python has become one of the most widely used and fastest-growing scientific programming languages by combining an accessible, high-level syntax with the availability of powerful third-party tools that facilitate rapid development and collaboration \cite{MullEtal15}. The Python ecosystem offers an extensive data science toolkit, including platforms for interactive programming (e.g., Project Jupyter, \cite{KluyEtal16}; Google Colaboratory), community-maintained libraries for data manipulation (e.g., \texttt{NumPy} \cite{HarrEtal20}, \texttt{SciPy} \cite{VirtEtal20}, \texttt{Pandas} \cite{McKi10}) and visualization (e.g., \texttt{Matplotlib} \cite{Hunt07}, \texttt{seaborn} \cite{Wask21}), and myriad other tools. However, this also presents a challenge to writing and sharing stable, reproducible scientific Python code: different versions of the same third-party library may behave differently, use different syntax, add or drop support for specific functions or other libraries, address (or introduce) bugs, and so on. While these issues are present to some extent in any language or ecosystem, they have a particular impact on the Python community due to its unusually rapid growth relative to other languages. Ensuring consistent behavior over time and across users therefore typically requires ensuring that Python code is always run with a specific set of versions for each package used.

One common approach to solving this problem is to create containerized or virtualized Python environments (e.g., using \href{https://www.docker.com/}{Docker}, \href{https://sylabs.io/singularity/}{Singularity}, or \href{https://docs.conda.io/en/latest/}{conda}) tailored to individual applications. Researchers can then share these environments alongside their code as configuration files that explicitly list required packages and package versions, allowing others to build identical copies themselves. While powerful, this approach bears two significant drawbacks: First, it adds to the
